
---
title: "Homework 1"
author: "Ramon Hernandez"
date: "2023-02-20"
output: 
  html_document:
    theme:  readable
---
```{r ,echo=FALSE}
library(pander)
data(swiss)
```
```{r variables, echo=FALSE}
numprov <- 47
studydate <- 1888
```


## <span style="color:darkblue">Swiss Fertility Data Set (`r studydate`)</span>

Switzerland, in 1888, was entering a period known as the demographic transition; i.e., its fertility was beginning to fall from the high level typical of underdeveloped countries.Mosteller, F. and Tukey, J. W. (1977) Data Analysis and Regression: A Second Course in Statistics. Addison-Wesley, Reading Mass.
indicating their source as “Data used by permission of Franice van de Walle. Office of Population Research, Princeton University, 1976. Unpublished data assembled under NICHD contract number No 1-HD-O-2077.”



### <span style="color:darkblue">Data </span>

```{r ,echo=FALSE}
pander((swiss[ , c(1,4,5)]), split.tables = 120)
```



```{r, echo=FALSE}
x <- round(mean(swiss$Fertility), 2)
xmn <- round(min(swiss$Fertility), 2)
xm <- round(max(swiss$Fertility), 2)
y <- round(mean(swiss$Education), 2)
ymn <- round(min(swiss$Education), 2)
ym <- round(max(swiss$Education), 2)
z <- round(mean(swiss$Catholic), 2)
```



## <span style="color:darkblue">Maternity Averages </span>
### <span style="color:darkblue">Fertility (`r x`)</span>
### <span style="color:darkblue">Education (`r y`)</span>
### <span style="color:darkblue">Catholic (`r z`)</span>


### <span style="color:darkblue">**Education and Fertility**</span>

#####  Looking specifically at the relationship between `Education` and `Fertility`, we can see that `Fertility` generally decreases as `Education` increases (see graph below). As we observed in the summary table above, the minimum and maximum values of `Fertility` are `r xmn` and `r xm`, respectively; the minimum and maximum values of `Education` are `r ymn`% and `r ym`%, respectively. 

```{r twowayA, echo=FALSE}
plot(swiss$Education, swiss$Fertility, xlab="Education (% beyond primary school, adults)", ylab="Fertility (index)", main="Fertility vs. Education", frame.plot=FALSE , col="cornflowerblue")
```



```{r twowayB, echo=FALSE}
plot(swiss$Catholic, swiss$Fertility, xlab="Catholic (% beyond primary school, adults)", ylab="Fertility (index)", main="Fertility vs. Catholic", frame.plot=FALSE , col="cornflowerblue")
```


